Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-12 edubots_surveys.Rnw
Rewriting via ChatGPT again

One of the most interesting questions arising from the analysis of the results,
and that should require further study, is: Are teachers really aware of the
possibilities of chatbots in the classroom? The survey only listed a few
functionalities for the chatbots, and just a few subjects selected the option
``Others''. This may suggest that most teachers did not really understand at
this point the actual potential of chatbots, since the responses listed were by
no means exhaustive. Had the responders been more acquainted with the
possibilities of this technology, this ``Other'' response would possibly have
shown up many more times. Another way to look at it is that, unless you provide
the specific instructions on how to use a tool, the teaching staff is already
too busy or burnt out to think about innovation, so they likely considered that it was not their
job to think about new possibilities of existing or new technologies.

>>>>

One of the most interesting questions arising from the analysis of the results,
and that should require further study, is: Are teachers really aware of the
possibilities of chatbots in the classroom? The survey only listed a few
functionalities for the chatbots, and just a few subjects selected the option
``Others''. This may suggest that most teachers did not really understand at
this point the actual potential of chatbots, since the responses listed were by
no means exhaustive. Had the responders been more acquainted with the
possibilities of this technology, this ``Other'' response would possibly have
shown up many more times. Another perspective is that, without clear guidelines on how to utilize a tool, educators may not have the capacity or energy to consider innovative uses; thus, they may have assumed that it is not their responsibility to explore new possibilities with existing or new technologies.
